Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-03-18 reports/rmarkdown/manuscript/manuscript_template.Rmd
adds metadata on umap and cytokine and IF plots

```{r, echo = FALSE, eval = TRUE,fig.asp=1.2}

@@

>>>>

```{r, echo = FALSE, eval = TRUE,fig.asp=.5}
figlabels <- letters

cytokine_data <- read.csv("../../../data/210125_Cytokines_visit3CVL.csv")
cytokine_data$ID <- metadata [ match( cytokine_data$PatID , as.character(metadata$PatID)  ) ,"ID" ]
cytokine_data <- cytokine_data[ !is.na(cytokine_data$ID) , ]
rownames(cytokine_data) <- cytokine_data$ID
cytokine_data <- cytokine_data[,grepl("CVL",colnames(cytokine_data))]
colnames(cytokine_data) <- sub("CVL_","",colnames(cytokine_data))
cytokine_data <- t(cytokine_data)
cytokine_data[is.na(cytokine_data)] <- 0.35
cytokine_data <- log2(cytokine_data+1)

groupings <- metadata$group_annotation [ match( colnames(cytokine_data) , as.character(metadata$ID)  ) ]
mypar(1,3,mar=c(6,5,1,5))

plot_dots(data=cytokine_data,
          srt=45,
          genes=rownames(cytokine_data),
          col = pal,
          clustering=groupings )
add_letter(figlabels[1]); figlabels <- figlabels[-1]

barlist(data=cytokine_data,
          srt=45,
          genes=rownames(cytokine_data),
          col = pal,
          clustering=groupings )
add_letter(figlabels[1]); figlabels <- figlabels[-1]

violist(data=cytokine_data,
          srt=45,
          genes=rownames(cytokine_data),
          col = pal, transparency = 50,
          clustering=groupings,smooth = 2 )
add_letter(figlabels[1]); figlabels <- figlabels[-1]

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=.8}
figlabels <- letters

IF_data <- read.csv("../../../data/200105_CD4Ecad_Visit3LAMIQ.csv")
IF_data$ID <- metadata [ match( IF_data$PatID , as.character(metadata$PatID)  ) ,"ID" ]
IF_data <- IF_data[ !is.na(IF_data$ID) , ]
rownames(IF_data) <- IF_data$ID
IF_data <- IF_data [ , -c(1:3)]
IF_data <- IF_data [ , -ncol(IF_data)]
IF_data <- t(IF_data)
# IF_data[is.na(IF_data)] <- 0
# IF_data <- log2(IF_data+1)

groupings <- metadata$group_annotation [ match( colnames(IF_data) , as.character(metadata$ID)  ) ]

mypar(1,3,mar=c(6,15,1,4))
plot_dots(data=IF_data,
          srt=45,
          genes=rownames(IF_data),
          col = pal,
          clustering=groupings )
add_letter(figlabels[1]); figlabels <- figlabels[-1]

barlist(data=IF_data,
          srt=45,
          genes=rownames(IF_data),
          col = pal,
          clustering=groupings )
add_letter(figlabels[1]); figlabels <- figlabels[-1]

violist(data=IF_data,
          srt=45,
          genes=rownames(IF_data),
          col = pal, transparency = 50,
          clustering=groupings,smooth = 2 )
add_letter(figlabels[1]); figlabels <- figlabels[-1]

```{r, echo = FALSE, eval = TRUE,fig.asp=.5}

continuous_parameters <- c("age","Count_CD4_v2","Count_CD4_v3","Plasma_S_Prog_ng_mL_v3","Plasma_S_Estradiol_pg_mL_v3","Conc_T4_v2","Conc_T3_v2","Conc_Progesteron_v2","Conc_Estradiol_v2","Conc_Cortisol_v2","Freq_CD4_v2","Freq_CD4_v3","Freq_Lympho_v2","Freq_Lympho_v3","visit_clients7days_v2")

mypar(1,3,mar=c(6,15,1,4))
plot_dots(data=as.matrix(t(metadata[,continuous_parameters])),
          srt=45,
          genes=continuous_parameters,
          col = pal,
          clustering=metadata$group_annotation )
add_letter(figlabels[1]); figlabels <- figlabels[-1]

barlist(data=as.matrix(t(metadata[,continuous_parameters])),
          srt=45,
          genes=continuous_parameters,
          col = pal,
          clustering=metadata$group_annotation )
add_letter(figlabels[1]); figlabels <- figlabels[-1]

violist(data=as.matrix(t(metadata[,continuous_parameters])),
          srt=45,
          genes=continuous_parameters,
          col = pal, transparency = 50,
          clustering=metadata$group_annotation,smooth = 2 )
add_letter(figlabels[1]); figlabels <- figlabels[-1]

## Figure S11

```{r, echo = FALSE, eval = TRUE,fig.asp=1.2}
figlabels <- letters

g <- graph_from_adjacency_matrix(as.matrix(SNN_patients), mode = "undirected",diag = F,weighted = T)
set.seed(1)
l <- layout_with_fr(g,niter=3000,start.temp=30)

continuous_parameters <- c("age","Count_CD4_v2","Count_CD4_v3","Plasma_S_Prog_ng_mL_v3","Plasma_S_Estradiol_pg_mL_v3","Conc_T4_v2","Conc_T3_v2","Conc_Progesteron_v2","Conc_Estradiol_v2","Conc_Cortisol_v2","Freq_CD4_v2","Freq_CD4_v3","Freq_Lympho_v2","Freq_Lympho_v3","visit_clients7days_v2")

mypar(6,6,mar=c(1,1,1,1))

plot(l,
       col=pal[metadata$group_annotation],
       main=i,xpd=T,
       pch=16,xlab="",ylab="",frame=F,axes=F,font.main=1,cex.main=1)
empty_plot()
legend("topleft",title.adj = 0,
       legend = levels(metadata$group_annotation),xjust = 0,yjust = 1,
       bty = "n",pch = 16,col = pal,pt.cex = 1,xpd=T)

for(i in continuous_parameters){
  xx <- metadata[,i]
  xx[is.na(xx)] <- 0
  xx <- xx / max(xx)
  o <- order(xx)
  plot(l[o,],
       col=colorRampPalette( c("grey95","navy")) (99)[ 1 + (xx[o]*98) ],
       main=i,xpd=T,
       pch=16,xlab="",ylab="",frame=F,axes=F,font.main=1,cex.main=1)

## Figure S12

```{r, echo = FALSE, eval = TRUE,fig.asp=1.2}
figlabels <- letters

g <- graph_from_adjacency_matrix(as.matrix(SNN_patients), mode = "undirected",diag = F,weighted = T)
set.seed(1)
l <- layout_with_fr(g,niter=3000,start.temp=30)

categorical_parameters <- c("Antibiotics","Antibiotics_v2","Antibiotics_v3",
                         "Bacterio_KOH_v2","Bacterio_KOH_v3","Bacterio_TV_v3",
                         "BV_Clue_Cells_v2","BV_Clue_Cells_v3",
                         "BV_Diagnosis_v2","BV_Diagnosis_v3",
                         "BV_Lactobacillus_v2","BV_Lactobacillus_v3",
                         "BV_Monbilicus_v2","BV_Monbilicus_v3",
                         "BV_Vaginal_Garda_v2","BV_Vaginal_Garda_v3",
                         "blood_cervix_v2","blood_cervix_v3",
                         "cervical_inflammation_v2","cervical_inflammation_v3",
                         "HIVstatus","Contraception",
                         "CT_v2","CT_v3","regular_partner",
                         "vaginal_douching_v2","vaginal_douching_v3")

mypar(6,5,mar=c(1,1,1,8))
plot(l,
       col=pal[metadata$group_annotation],
       main=i,xpd=T,
       pch=16,xlab="",ylab="",frame=F,axes=F,font.main=1,cex.main=1)
legend(par("usr")[2],par("usr")[4],title.adj = 0,
       legend = levels(metadata$group_annotation),xjust = 0,yjust = 1,
       bty = "n",pch = 16,col = pal,pt.cex = 1,xpd=T)

for(i in categorical_parameters){
  xx <- factor(metadata[,i])
  plot(l[,],
       col=pal[xx],
       main=i,xpd=T,
       pch=16,xlab="",ylab="",frame=F,axes=F,font.main=1,cex.main=1)
legend(par("usr")[2],par("usr")[4],title.adj = 0,
       legend = levels(xx),xjust = 0,yjust = 1,
       bty = "n",pch = 16,col = pal,pt.cex = 1,xpd=T)
}
```

## Figure S13

### 2021-03-18 reports/rmarkdown/manuscript/manuscript_template.tex
adds metadata on umap and cytokine and IF plots

\title{Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A demonstration of Rmarkdown using Herman Bumpus' data}
\author{Author One\textsuperscript{1},
Author Two\textsuperscript{2},
Author Three\textsuperscript{1,2}}
\date{March 12, 2021}

@@

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-20-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-20-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-20-3}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-20-4}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-20-5}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-20-6}

>>>>

\title{Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A demonstration of Rmarkdown using Herman Bumpus' data}
\author{Author One\textsuperscript{1},
Author Two\textsuperscript{2},
Author Three\textsuperscript{1,2}}
\date{March 18, 2021}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-19-1}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-20-1}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-21-1}

\hypertarget{figure-s11}{%
\subsection{Figure S11}\label{figure-s11}}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-22-1}

\hypertarget{figure-s12}{%
\subsection{Figure S12}\label{figure-s12}}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-23-1}

\hypertarget{figure-s13}{%
\subsection{Figure S13}\label{figure-s13}}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-3}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-4}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-5}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-6}
